Fusion Moves for Correlation Clustering

### 2014-11-11 paper/inputs/fig_hc_alg.tex

\begin{center}
\begin{figure*}
\resizebox{!}{0.15\linewidth}{%
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,2) node[nS] (n0) {$0$}; 
    \draw (4,2) node[nS] (n1) {$1$};
    \draw (6,2) node[nS] (n2) {$2$};
    \draw (2,0) node[nS] (n3) {$3$}; 
    \draw (4,0) node[nS] (n4) {$4$};
    \draw (6,0) node[nS] (n5) {$5$};

    \path
        (n0) edge[eCut] node[eNS]{$w_{01}=-1$} (n1) 
        (n1) edge[eCut] node[eNS]{$w_{12}=-2$} (n2) 
        (n3) edge[eCut] node[eNS]{$w_{34}=-2$} (n4) 
        (n4) edge[eCut] node[eNS]{$w_{45}=1$} (n5)
        (n0) edge[eNotCut] node[eNS]{$w_{03}=4$} (n3)
        (n1) edge[eCut] node[eNS]{$w_{14}=2$} (n4)
        (n2) edge[eCut] node[eNS]{$w_{25}=3$} (n5)
    ;
    \end{tikzpicture}
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4,2) node[nS] (n1) {$1$};
    \draw (6,2) node[nS] (n2) {$2$};
    \draw (4,0) node[nS] (n4) {$4$};
    \draw (6,0) node[nS] (n5) {$5$};

    \path
        (n03) edge[eCut] node[eNS]{$w_{01}=-1$} (n1) 
        (n1) edge[eCut] node[eNS]{$w_{12}=-2$} (n2) 
        (n03) edge[eCut] node[eNS]{$w_{34}-2$} (n4) 
        (n4) edge[eCut] node[eNS]{$w_{45}=1$} (n5)
        (n1) edge[eCut] node[eNS]{$w_{14}=2$} (n4)
        (n2) edge[eNotCut] node[eNS]{$w_{25}=3$} (n5)
    ;
    \end{tikzpicture}
}
%
\resizebox{!}{0.15\linewidth}{%
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4,2) node[nS] (n1) {$1$};
    \draw (6,1) node[nS] (n25) {$\{2,5\}$};
    \draw (4,0) node[nS] (n4) {$4$};
    \path
        (n03) edge[eCut] node[eNS]{$w_{01}=-1$} (n1) 
        (n1) edge[eCut] node[eNS]{$w_{12}=-2$} (n25) 
        (n03) edge[eCut] node[eNS]{$w_{34}=-2$} (n4) 
        (n4) edge[eCut] node[eNS]{$w_{45}=1$} (n25)
        (n1) edge[eNotCut] node[eNS]{$w_{14}=2$} (n4)
    ;
    \end{tikzpicture}
    \begin{tikzpicture}
    \draw (0,-1)node (dummyLow){} ;
    \draw (0, 3)node (dummyLow){} ;
    \draw (2,1) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4,1) node[nS] (n14) {$\{1,4\}$};
    \draw (6,1) node[nS] (n25) {$\{2,5\}$};
    \path
        %(n03) edge[eCut] node[eNS]{$w_{01}$} (n1) 
        (n14) edge[eBlue] node[eNS]{$w_{12}+$\\$w_{45}=$\\$-1$} (n25) 
        (n03) edge[eCut] node[eNS]{$w_{01}+$\\$w_{34}=$\\$-3$} (n14) 
    ;
    \end{tikzpicture}
}
\caption{
     To use hierarchical clustering as an approximator for
    the multicut objective we contract the edge with the highest weight
    in each step (to be contracted edge is shown in green).
    Whenever multiple edges are merged into a single edge,
    we use the sum of the weight as a new weight, since
    we have to pay for all edges which are cut in the uncontracted
    graph.
    We stop when the highest edge weight is smaller
    or equal to zero (edge shown in blue).
}\label{fig:hc_alg}
\end{figure*}
\end{center}

>>>>

\begin{center}
\begin{figure}
\begin{center}
\resizebox{0.75\linewidth}{!}{
%\resizebox{!}{0.25\linewidth}{%
    \begin{tikzpicture}
    %\draw (0,-1)node (dummyLow){} ;
    %\draw (0, 3)node (dummyLow){} ;
    \draw (2,2) node[nS] (n0) {$0$}; 
    \draw (4,2) node[nS] (n1) {$1$};
    \draw (6,2) node[nS] (n2) {$2$};
    \draw (2,0) node[nS] (n3) {$3$}; 
    \draw (4,0) node[nS] (n4) {$4$};
    \draw (6,0) node[nS] (n5) {$5$};

    \path
        (n0) edge[eCut] node[eNS]{$w_{01}=-1$} (n1) 
        (n1) edge[eCut] node[eNS]{$w_{12}=-2$} (n2) 
        (n3) edge[eCut] node[eNS]{$w_{34}=-2$} (n4) 
        (n4) edge[eCut] node[eNS]{$w_{45}=1$} (n5)
        (n0) edge[eNotCut] node[eNS]{$w_{03}=4$} (n3)
        (n1) edge[eCut] node[eNS]{$w_{14}=2$} (n4)
        (n2) edge[eCut] node[eNS]{$w_{25}=3$} (n5)
    ;

    %\draw (0+6,-1)node (dummyLow){} ;
    %\draw (0+6, 3)node (dummyLow){} ;
    \draw (2+6,1) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4+6,2) node[nS] (n1) {$1$};
    \draw (6+6,2) node[nS] (n2) {$2$};
    \draw (4+6,0) node[nS] (n4) {$4$};
    \draw (6+6,0) node[nS] (n5) {$5$};

    \path
        (n03) edge[eCut] node[eNS]{$w_{01}=-1$} (n1) 
        (n1) edge[eCut] node[eNS]{$w_{12}=-2$} (n2) 
        (n03) edge[eCut] node[eNS]{$w_{34}-2$} (n4) 
        (n4) edge[eCut] node[eNS]{$w_{45}=1$} (n5)
        (n1) edge[eCut] node[eNS]{$w_{14}=2$} (n4)
        (n2) edge[eNotCut] node[eNS]{$w_{25}=3$} (n5)
    ;

    %\draw (0,-1)node (dummyLow){} ;
    %\draw (0,3-3)node (dummyLow){} ;
    \draw (2,1-3) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4,2-3) node[nS] (n1) {$1$};
    \draw (6,1-3) node[nS] (n25) {$\{2,5\}$};
    \draw (4,0-3) node[nS] (n4) {$4$};
    \path
        (n03) edge[eCut] node[eNS]{$w_{01}=-1$} (n1) 
        (n1) edge[eCut] node[eNS]{$w_{12}=-2$} (n25) 
        (n03) edge[eCut] node[eNS]{$w_{34}=-2$} (n4) 
        (n4) edge[eCut] node[eNS]{$w_{45}=1$} (n25)
        (n1) edge[eNotCut] node[eNS]{$w_{14}=2$} (n4)
    ;

    %\draw (0+6,-1 -3)node (dummyLow){} ;
    %\draw (0+6, 3 -3)node (dummyLow){} ;
    \draw (2+6,1  -3) node[nS] (n03) {$\{0,3\}$}; 
    \draw (4+6,1  -3) node[nS] (n14) {$\{1,4\}$};
    \draw (6+6,1  -3) node[nS] (n25) {$\{2,5\}$};
    \path
        %(n03) edge[eCut] node[eNS]{$w_{01}$} (n1) 
        (n14) edge[eBlue] node[eNS]{$w_{12}+$\\$w_{45}=$\\$-1$} (n25) 
        (n03) edge[eCut] node[eNS]{$w_{01}+$\\$w_{34}=$\\$-3$} (n14) 
    ;

    \end{tikzpicture}
%}

}
\caption{
    Hierarchical clustering can be used to optimize
    Eq.~\ref{eq:edgeproblem}.
    In each step, the two nodes connected via the edge with 
    the highest weight are merged by contracting this edge.
    (to be contracted edge is shown in green).
    Due to edge contraction parallel edges can occur which 
    are merged into single ones, and their weights are summed up.
    The algorithm stops when the highest edge weight is smaller
    or equal to zero (edge shown in blue).
}\label{fig:hc_alg}
\end{center}
\end{figure}
\end{center}
